Memories of migrations past: Sociality and cognition in dynamic, seasonal environments

### 2021-07-16 text/SocialMemoryMigration_FEE.tex
...

	Migratory species may be more vulnerable to environmental change as disruption in either of the seasonal ranges or along a migratory corridor can have significant negative impacts \citep{Wilcove2008, Kauffman2021}. On the other hand, migratory species might be more resilient to large-scale disruptions due to their wide-ranging mobility \citep{Robinson2009}. A long-distance migration can not rely entirely on local cues, and is therefore only possible if the behavior is hard-programmed or remembered. On the other hand, a strictly programmed behavior can be maladaptive if conditions change.While migration can clearly be a highly successful strategy, the resilience of migratory populations and migratory behavior is an open question and depends on the plasticity and adaptability of a population \citep{Xu2021}.  That plasticity can take multiple forms, reflecting variation in \textit{where}, \textit{when} and \textit{whether} the migration occurs \citet{Gurarie2017,Xu2021}.

>>>>

	Migratory species may be more vulnerable to environmental change as disruption in either of the seasonal ranges or along a migratory corridor can have significant negative impacts \citep{Wilcove2008, Seebacher2015, Kauffman2021}. On the other hand, migratory species might be more resilient to large-scale disruptions due to their wide-ranging mobility \citep{Robinson2009}, and the cognitive and social factors determining the resilience of migrations to climate change are generally unknown. A long-distance migration can not rely entirely on local cues, and is therefore only possible if the behavior is hard-programmed or remembered. On the other hand, a strictly programmed behavior can be maladaptive if conditions change.While migration can clearly be a highly successful strategy, the resilience of migratory populations and migratory behavior is an open question and depends on the plasticity and adaptability of a population \citep{Xu2021}.  That plasticity can take multiple forms, reflecting variation in \textit{where}, \textit{when} and \textit{whether} the migration occurs \citet{Gurarie2017, Xu2021}.
